{\Huge Supersymmetry} \\ \vspace{5mm} Lecture notes for FYS5190/FYS9190 Supersymmetry

### 2023-09-23 groups.tex

We have already seen multiple example of the exponential map construction, but we may ask, why use the exponential? One reason is that it gives us a natural expansion of the group around the identity element. With the parameters $\mathbf a=0$ the resulting matrix is the identity matrix, which means that the group element is the identity element $g=e$. Similarly, for an infinitesimal $d\mathbf a$ step away from the parameters of the identity we have the group elements near the identity, $g=I+ida_iX^i$ that we used to derive the generators. And now, if we apply a small finite step  $a_i$ away from the identity $g=I+i\frac{a_i}{n}X^i$ a total of $n$ times with smaller and smaller steps we will get
\[g=\left(I+i\frac{a_i}{n}X^i\right)^n. \]
By the limit definition of the exponential, for $n\to\infty$ this is the exponential map
\[g=\lim_{n\to\infty}\left(I+i\frac{a_i}{n}X^i\right)^n=\exp( ia_iX^i). \]

>>>>

We have already seen multiple example of the exponential map construction, but we may ask, why use the exponential? One reason is that it gives us a natural expansion of the group around the identity element. With the parameters $\mathbf a=0$ the resulting matrix is the identity matrix, which means that the group element is the identity element $g=e$. Similarly, for an infinitesimal $d\mathbf a$ step away from the parameters of the identity we have the group elements near the identity, $g=I+ida_iX^i$ that we used to derive the generators. And now, if we apply a small finite step  $a_i$ away from the identity $g=I+i\frac{a_i}{n}X^i$ a total of $n$ times we will get
\[g=\left(I+i\frac{a_i}{n}X^i\right)^n. \]
By the limit definition of the exponential, with smaller and smaller steps letting $n\to\infty$ this is the exponential map
\[g=\lim_{n\to\infty}\left(I+i\frac{a_i}{n}X^i\right)^n=\exp( ia_iX^i). \]
